# Example 1
```{r}
marbles = c('red', 'blue', 'green')
sample(x = marbles, size = 2, replace = F)
```

```{r}
sample(x = 1:10, size = 5, replace = FALSE)
numbers = 1:10
sample(x = numbers, size = 20, replace = TRUE)
```

#Ex1. I’m running a prize drawing and need to select two different students from Econ 103 at random.
```{r}
students = c("Alice", "Bob", "Charlotte", "Dan", "Emily")
sample(x = students, size = 2, replace = FALSE) 
```

#Ex2. Jim is bored and loves to solve math problems for fun. (He’s a strange guy.) To pass the time, he labels ten cards with the numbers 1 through 10 and puts them in a bowl. He then draws five of these cards with replacement and calculates their sum. Use R to replicate one of Jim’s “random sums.”
```{r}
random.numbers = sample(x = 1:10, size = 5, replace = TRUE)
sum(random.numbers)
```

#Ex3. roll two fair, six-sided dice and compute their sum?
```{r}
sample(1:6, size = 1, replace = TRUE) + sample(1:6, size = 1, replace = TRUE)

#But it turns out that there’s a much easier way:
dice.roll <- sample(1:6, size = 2, replace = TRUE)
dice.roll
sum(dice.roll)

#or, in a single command:
sum(sample(1:6, size = 2, replace = TRUE))

#Write R code to roll ten fair, six-sided dice and calculate their sum
sum(sample(x = 1:6, size = 10, replace = TRUE))

```

# make a function to roll two fair, six-sided dice and return their sum as follows:
```{r}
two.dice <- function(){
  dice <- sample(1:6, size = 2, replace = TRUE)
  return(sum(dice))
}

two.dice()
```

# To use replicate, we need to specify two arguments: n tells R how many times we want to repeat something and expr is the R command we want to repeat.
```{r}
replicate(n = 20, expr = two.dice())

# returning a vector
replicate(10, sample(1:10, 1, replace = FALSE))

# returning a matrix
replicate(10, sample(1:10, 5, replace = FALSE))
```












