# Date - 21 March 2019
# Description - Monte Carlo Simulations in R (trying out JourneyOfAnalytics codes)

```{r}
# Laod library packages:
library(data.table)

# set global options:
options(scipen = 999999)   # we don't want to use scientific notation .
options(digits = 4)   # we want only 2 digits after the decimal.

```
# Basic Monte Carlo code: 
```{r}
runs <- 100000
sims <- rnorm(runs,mean=4,sd=10)
mcmc_val <- sum(sims >= 3 & sims <= 6)/runs
cat(mcmc_val,'\n')
```

# For a given group of 8th grade male students, the average weight
# is 160 pounds and the standard deviation is 5.5 pounds. What is the probability
# that a student weighs over 205 pounds if we were to sample 5000 similar students?
```{r}
runs <- 5000
sims <- rnorm(runs,mean=160,sd=5.5)
mcmc_val <- sum(sims >= 205)/runs
cat(mcmc_val)
```
# Probability for weight of student >= 165 pounds.
```{r}
runs <- 5000
sims <- rnorm(runs,mean=160,sd=5.5)
mcmc_val <- sum(sims >= 165)/runs
cat(mcmc_val)
```
# Probability of getting more than 6 heads if we flip a coin 10 times.
# We conduct this experiemnt 10000
```{r}
runs <- 10000
coin_trial <- function(){
   sum(sample(c(0,1), size =10, replace = T)) > 6
}
coin_flips <- sum(replicate(runs, coin_trial())) / runs
cat(coin_flips)
```
# Assume 3 dice are rolled simultaneousely. What is the probability of 
# getting 6 on all 3 dice ?
```{r}
runs_500k <- 500000
dice_roll <- function(){
   x = sample(1:6, size =3, replace = T)
   # x
   # x >= 6
   # (sum(x >= 6)/3) == 1
   return( (sum(x >= 6)/3) == 1)
}
sum(replicate(runs_500k, dice_roll())) / runs_500k

runs_500k <- 500000
dice_roll <- function(){
   x = sample(1:6, size =1, replace = T)
   y = sample(1:6, size =1, replace = T)
   z = sample(1:6, size =1, replace = T)
   condition <- sum((x == y) & (y == z) & (x == z) & x == 6) > 0
   return(condition)
}
sims <- replicate(runs_500k, dice_roll())
sum(sims)/length(sims)
```
```{r}
table(sims)/length(sims)
plot(table(sims)/length(sims), xlab='Sum', ylab='Relative probability', main = '1 Roll of 3 Fair Dice and all 3 show up as a 6')
```






